Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2014-12-22 Paper/paper.tex
fix typos

Verbargs is the subset of Google's syntactic-ngram corpus for training our 
models and evaluating the reults 
A syntactic-ngram is a $k$-word rooted subtree of some sentence.
The ngrams in Google's corpus were extracted from 3.5 million books and are labled with
Penn Treebank part-of-speech tags Stanford-basic dependency lables \citep{ngrams2013}.
Each ngram also includes frequency counts by year.
In this project, used the

The ngrams in the verbargs dataset (130M items) consist of a verb and all of its 
immediate arguments.
From this dataset, we consider only VSO's, that is; we pruned verbargs to only
those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
is the ngram's root verb (1.6M items, 96M by count). 
We further trimmed the data to consider only the \%25 most common verbs 
(800K items, 78M by count).

@@

\section{Future Work}
One big weakness of this project over the results of \citet{oconnor2013} is that 
we could not used document-level context to leverage semantic information.
A possible direction of future reseach is to create models that take better 
advantage of the syntax-level context provided by syntactic ngrams. 
One easy way to do this would be to modify model 1 so that the argument 
vocabulary ranges over subject/object pairs instead of individual nouns.
or object.
More advanced models would take better advantage of the various kinds of arguments
in verbargs and their relation to one another.
For example, you might be gleen some semantic information about the relationship between
verbs and prepositional objects by the preposition that mediates them: 
That you ''swim \emph{in} the lake'' versus ``ice skate \emph{on} the lake'' 
indicates that the relationship between swimming and lakes is different from the one between
ice skating and lakes.

>>>>

A syntactic-ngram is a $k$-word rooted subtree of some sentence.
Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
books and labled with Penn Treebank part-of-speech tags Stanford-basic dependency 
lables \citep{ngrams2013}.
Each ngram also includes frequency counts by year.

This project uses the verbargs subeset (130M items) of Google syntactic-ngrams.
An ngram in the verbargs dataset consist of a verb and all of its 
immediate arguments.
We considered only the VSO's in this dataset, that is; we pruned verbargs to
those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
is the ngram's root verb (1.6M items, 96M by count). 
We further trimmed the data to consider only the \%25 most common verbs 
(800K items, 78M by count).

@@

\section{Future Work}
One big weakness of this project over the results of \citet{oconnor2013} is that 
we could not used document-level context to infer semantic information.
A possible direction of future reseach is to create models that take better 
advantage of the syntax-level context provided by syntactic ngrams. 
One easy way to do this would be to modify model 1 so that the argument 
vocabulary ranges over subject/object pairs instead of individual nouns.
or object.
More advanced models might take better advantage of the various kinds of arguments
in the verbargs dataset and their relation to one another.
For example, you could be gleen some semantic information about the relationship between
verbs and prepositional objects by looking at the preposition that mediates them: 
That you ''swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
indicates that the relationship between swimming and lakes is different from the one between
ice skating and lakes.
